The \dealii Library, Version 9.1

### 2019-05-20 9.1/paper.tex
Add my authorship info.
Summarize incompatible changes.
This list is a bit subjective: I suspect users are not using some of the
changed interfaces that deal with, e.g., implementing hp FEM.

\author[9]{David Wells}
\affil[9]{Department of Mathematical Sciences, Rensselaer Polytechnic
  Institute, Troy, NY 12180, USA.
  {\texttt{wellsd2@rpi.edu}}}

@@

\marginpar{Update after the release}
The 9.1 release includes
\href{https://dealii.org/developer/doxygen/deal.II/changes_between_9_0_1_and_9_1_0.html}
     {around 15 incompatible changes}; see \cite{changes91}. The majority of these changes
should not be visible to typical user codes; some remove previously
deprecated classes and functions, and the majority change internal
interfaces that are not usually used in external
applications. However, some are worth mentioning:
\begin{itemize}
\item TODO
\end{itemize}

>>>>

\author[9]{David Wells}
\affil[9]{Department of Mathematics, University of North Carolina,
  Chapel Hill, NC 27516, USA.
  {\texttt{drwells@email.unc.edu}}}

@@

The 9.1 release includes
\href{https://dealii.org/developer/doxygen/deal.II/changes_between_9_0_1_and_9_1_0.html}
     {around 15 incompatible changes}; see \cite{changes91}. The majority of these changes
should not be visible to typical user codes; some remove previously
deprecated classes and functions, and the majority change internal
interfaces that are not usually used in external
applications. However, some are worth mentioning:
\begin{itemize}
\item The \texttt{VectorView} class was removed. We recommend either copying the
      vector subset into a \texttt{Vector} or using a \texttt{BlockVector}.
\item The function \texttt{Subscriptor::subscribe} now requires a pointer to a
      \texttt{std::atomic<bool>} that tracks whether or not the pointer to the
      subscribed-to object is still valid.
\item The \texttt{ConstraintMatrix} class gained a template parameter for scalar
      type and was been renamed \texttt{AffineConstraints}. Several methods that
      take vectors or matrices as arguments,
      such as \texttt{AffineConstraints::distribute\_local\_to\_global()},
      now require that all matrix and vector arguments have matching number
      types.
\item Similarly, the functions \texttt{create\_mass\_matrix} and
      \texttt{create\_boundary\_mass\_matrix} in the \texttt{MatrixCreator}
      namespace no longer
      support matrix and vector objects of different types.
\end{itemize}
